Modeling Soot in Oxy-Coal Combustion Systems using Large Eddy Simulations

### 2020-01-14 manuscript/manuscript.tex
adding figures and modifying the manuscript

%====================================================================
\begin{abstract} % not to exceed 200 words
    Soot in coal combustion simulations is often ignored due to its computational complexity, despite its significant effect on flame temperature and radiation.  In this research, soot formation was investigated using Large Eddy Simulations (LES).  Simulations were performed for a 40 kW pilot-scale coal combustor and compared to published experimental data.  Soot was modeled using a detailed monodisperse soot model that was recently developed.  Future work will compare current simulations with new simulations that neglect soot in order to determine the effect of soot on flame properties.  
\end{abstract}

@@

>>>>

%====================================================================
\begin{abstract} % not to exceed 200 words
    Soot in coal combustion simulations is often ignored due to its computational complexity, despite its significant effect on flame temperature and radiation.  In this research, a 40 kW oxy-coal combustion system is modeled using Large Eddy Simulations (LES) and a detailed monodisperse coal soot model. Cases where soot is modeled are compared with cases where soot is neglected to determine the accuracy benefits and computational costs of modeling soot.

\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
